FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-08-21 paper.tex
Gen prop kill outline is now all vector graphics
Add some edits from Ganesh

\Fp{} numbers use a finite number of bits to represent a spectrum of points along the real number line~(\cref{f:real-vs-fp}).
The implementation strategy is essentially scientific notation.
A \fp{} number packs a sign bit, an exponent, and a fraction part (also called the ``significand'' or ``mantissa'') into a bitstring.
Typical strings are 64 or 32 bits long, but 16-bit and 8-bit formats are on the rise~\cite{klowerLowprecisionClimateComputing2021,fp8}.
This representation supports very small and very large numbers in a narrow range of bits:

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/genpropkill-outline.pdf}
  \caption{Gen, Prop, Kill: Lifetime of an exceptional value}
  \label{f:gpk}
\end{figure}

@@

\Cref{fig:sw_nan_cstg} presents the stack graph for \NaN{} gen events
in shallow waters with the high CFL number.
Reading bottom-up, every \NaN{} came from calls to the \code{-} and \code{+} operations.
Calls to \code{+} account for most of the \NaN{}s.
These \NaN{}s arose in two different contexts: a small number (30)
occurred within a momentum calculation, while the rest (162)
occurred within a continuity step.
Moving to the top of the graph, it shows that the function \code{run\_model} drove
the entire simulation.
With this overview of the program, a promising next step is to guard against \NaN{}s
in the momentum and continuity functions.

@@

Thanks to the \code{Sherlogs.jl} developers for inspiring the architecture of \FT{}.
Thanks to the \code{RxInfer.jl} developers for testing \FT{} and for feedback on its user interface.
Thanks to Alex Larsen and Rob Durst for comments on an early draft.
This work is supported by
NSF grant \href{https://nsf.gov/awardsearch/showAward?AWD_ID=2030859&HistoricalAwards=false}{2030859}
to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.

>>>>

\Fp{} numbers use a finite number of bits to represent a spectrum of points along the real number line~(\cref{f:real-vs-fp}).
The implementation strategy is essentially that followed in scientific notation.
A \fp{} number packs a sign bit, an exponent, and a fraction part (also called the ``significand'' or ``mantissa'') into a bitstring.
Typical strings are 64 or 32 bits long, but 16-bit and 8-bit formats are on the rise~\cite{klowerLowprecisionClimateComputing2021,fp8}.
This representation supports very small and very large numbers in a narrow range of bits:

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/genpropkill-outline_vector.pdf}
  \caption{Gen, Prop, Kill: Lifetime of an exceptional value}
  \label{f:gpk}
\end{figure}

@@

\Cref{fig:sw_nan_cstg} presents the stack graph for \NaN{} gen events
in shallow waters with the high CFL number.
Reading bottom-up, every \NaN{} came from calls to the `\code{-}' and `\code{+}' operations.
Calls to `\code{+}' account for most of the \NaN{}s.
These \NaN{}s arose in two different contexts: a small number (30)
occurred within a momentum calculation, while the rest (162)
occurred within a continuity step.
Moving to the top of the graph, it shows that the function \code{run\_model} drove
the entire simulation.
With this overview of the program, a promising next step is to guard against \NaN{}s
in the momentum and continuity functions.

@@

Thanks to the \code{Sherlogs.jl} developers for inspiring the architecture of \FT{}.
Thanks to the \code{RxInfer.jl} developers for testing \FT{} and for feedback on its user interface.
Thanks to Alex Larsen and Rob Durst for comments on an early draft.
This work is supported by
NSF grant \href{https://nsf.gov/awardsearch/showAward?AWD_ID=2030859&HistoricalAwards=false}{2030859}
to the CRA for the \href{https://cifellows2020.org}{CIFellows} project,
and DOE ASCR Award Number DE-SC0022252 and NSF CISE Awards 1956106 and 21241.
